%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Staff Software Architect} % Job title
    {GE Healthcare} % Organization
    {Waukesha, Wisconsin} % Location
    {April 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{WPA Supplicant: Converted thousands of lines of GEHC additions to WPA supplicant (core and QT GUI) into atomic commits.}}
      \item {\textbf{FIPS: Investigated and documented Linux support for FIPS with detailed focus on Wi-Fi support.}}
      \item {\textbf{Implemented network container aware netlink based network state monitoring code.}}
      \item {\textbf{Improved Wi-Fi performance by patching Linux Wi-Fi Driver} to fully utilize all channels and capabilities allowed by regulatory domain. Patched driver compiled and packaged for SUSE via the 'Kernel Module Package' RPM spec.}
      \item {\textbf{Implementing code to properly configure IP Address and DNS from GUI} in coordination with wicked network manager (SUSE) and dnsmasq.}
      \item {\textbf{Implemented direct barcode scanner input to Java application} via direct connection to Linux input event subsystem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Engineer - OS Architect} % Job title
    {Johnson Controls} % Organization
    {Milwaukee, Wisconsin} % Location
    {Jan 2019 - April 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{Added display and proprietary input panel to Linux based embedded system.}
        Implemented SPI GPIO device driver for MAX6966 chip for input and backlight.
        Modified existing tinydrm display driver to drive display.
        Used Wayland protocol and compositor to drive the display.
        Wrote application code to connect to display and input device via Wayland interface.
        Diagnosed and resolved hardware issues to make the device work.
      }
      \item {\textbf{Analyzed, improved and determined limit of network performance in embedded system.}
        Identified multiple performance bottlenecks in specific IMX6 based embedded system.
        This included problems with SSL, limitations of the IMX6 network device, impact of packet loss on TCP performance, etc.
        Completed detailed analysis and documentation of Linux Work Queue as it related to IP stack and specific issues with the IMX6 device usecase and asymmetries between the ingress and egress paths.
        Tested various traffic shaping algorithms to reduce jitter and increase bi-directional throughput.
      }
      \item {\textbf{Implemented thermal resistance testing and power profiling framework in Python.}
        Implemented test framework and completed testing to determine thermal resistance (heat dissipation capacity) of system.
        Test framework executed various stress-ng tests on target while monitoring CPU temperature and power consumption over time.
        Python code interfaced with a Keithley DMM6500 in real time to measure power consumption of device under test.
        Testing results were used to compare and contrast thermal performance of new prototypes against the original system.
        Testing was able to show how long various tasks (example large file transfer) could execute at full CPU clock before thermal limits forced CPU throttling.
      }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Technical Consultant} % Job title
    {RedHat} % Organization
    % {Intel Next Generation Standards} % Organization
    {Remote} % Location
    {Jan 2018 - Jan 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Made open source contributions to the libvirt daemon adding support for QEMU / KVM virtualization features.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Staff Software Engineer} % Job title
    {Intel} % Organization
    % {Intel Next Generation Standards} % Organization
    {Lake Zurich, Illinois} % Location
    {2013 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{Improved competitiveness of Intel 4G Cellular Modem by
        significantly increasing IP data transfer rate and efficiency} by
          applying best practices from Linux Kernel and Networking Device
          Drivers to optimize Modem data path in collaboration with a
          multinational team of engineers.}
      \item {\textbf{Optimized architecture decisions by delivering new and
        unprecedented visualizations} of control flow during data transfers
          by creating custom programs (Ruby) to extract control flow graphs from ARM
          ETM trace data.}
        \item {\textbf{Accelerated architecture decisions by rapidly prototyping
          and profiling data transfers between virtual machines} to clarify performance expectations and optimize virtual machines and driver configurations.
          Created custom programs (Ruby) to configure virtual
          machines using libvirt + KVM, launched and execute data transfers between machines, and
          captured performance data using Linux 'perf tools'.}
        \item {\textbf{Optimized software decision making by creating a custom
          interactive visualization web app} allowing developers to fully understand the performance impact of decisions on a wide range of CPU performance metrics.
          Visualization Web App was created using D3, Angular and Rails.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Software Engineer} % Job title
    {Motorola Mobile Devices} % Organization
    {Libertyville, Illinois} % Location
    {1998 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{Delivered wireless internet access to millions of customers
        using Motorola Phones and 3G/4G Modems over many years.}
          Held increasing levels of responsibility starting as data network
          component developer progressing to responsibility for data networking
          architecture at top of Modem stack including IPv6, Network Device
          Drivers, Mobile IP, Modem API, Android Interfacing, VoIP, IMS, Wi-Fi and VPN.
          Leveraged Open Source and Linux whenever possible to deliver highly advanced feature sets with absolute minimum development cost.
          Supported and collaborated with multinational development teams to deliver solutions.}
        \item {\textbf{Provided a well functioning and stable cellular modem interface to customers.}
  Led change control board responsible for reviewing and approving public 4G Modem interface changes.  
  Delivered technical leadership for Modem's "Vendor RIL" interface to Android and Android data network functioning in general.}
        \item {\textbf{Improved competitiveness of Motorola 4G Cellular Modem by significantly increasing IP data transfer rate and efficiency} 
          by optimizing ARM11 Linux Kernel data path in Modem using recompiled kernels, Linux 'perf tools', and applying networking best practices.}
        \item {\textbf{Recognized for collaboration with multiple internal groups and Legal Team }
           in a successful defense of teams' work against a patent infringement claim.
           }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Prior to 1998} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Held progressively responsible positions with Sony, Phillips,
          Microware and Engineering Animation with accomplishments including the
          \textbf{creation of video capture hardware and software, MPEG2 video
          drivers, 2D graphics chip drivers and the creation of an extensive 2G
          graphics library for embedded devices.}}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
